sdmTMB: an R package for fast, flexible, and user-friendly generalized linear mixed effects models with spatial and spatiotemporal random fields

### 2022-11-04 doc/paper-jss/owls.Rmd
style new resid chunk

```{r stan-resids-owls, eval=FALSE}
fit_ml <- update(fit_owl, reml = FALSE)
mcmc_resids <- residuals(fit_owl, type = "mle-mcmc", mcmc_iter = 101, mcmc_warmup = 100)
```

>>>>

```{r stan-resids-owls, eval=FALSE}
fit_ml <- update(fit_owl, reml = FALSE)
mcmc_resids <- residuals(fit_owl,
  type = "mle-mcmc",
  mcmc_iter = 101,
  mcmc_warmup = 100
)
```
